An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-03 paper.tex
Authors and affiliations

\documentclass[twocolumn,10pt]{article}
\pdfoutput=1 % This must be in the first 5 lines to tell arXiv to use pdfLaTeX
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage[cm]{fullpage}
\usepackage{multirow}

@@

\title{An Empirical Analysis of the Internet Engineering Task Force 
       with Computational Methods}
\author{Mladen Karan \and
        Prashant Khare \and
        Ravi Shekhar \and
        Matthew Russell Barnes \and
        Waleed Iqbal \and
        Junaid Qadir \and
        Stephen McQuistin \and
        Richard G. Clegg \and
        Patrick Healey \and
        Matthew Purver \and
        Ignacio Castro \and
        Gareth Tyson \and
        Colin Perkins}

>>>>

\documentclass[twocolumn,10pt]{article}
\pdfoutput=1 % This must be in the first 5 lines to tell arXiv to use pdfLaTeX
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage[cm]{fullpage}
\usepackage{multirow}
\usepackage{authblk}

@@

\title{An Empirical Analysis of the Internet Engineering Task Force 
       with Computational Methods}
\author[1]{Mladen Karan}
\author[1]{Prashant Khare}
\author[2]{Ravi Shekhar}
\author[1]{Matthew Russell Barnes}
\author[1]{Waleed Iqbal}
\author[3]{Junaid Qadir}
\author[4]{Stephen McQuistin}
\author[1]{Richard G. Clegg}
\author[1]{Patrick Healey}
\author[5]{Matthew Purver}
\author[1]{Ignacio Castro}
\author[6]{Gareth Tyson}
\author[7]{Colin Perkins}

\affil[1]{Queen Mary University of London}
\affil[2]{University of Essex}
\affil[3]{Information Technology University}
\affil[4]{University of St Andrews}
\affil[5]{Jozef Stefan Institute}
\affil[6]{Hong Kong University of Science \& Technology}
\affil[7]{University of Glasgow}
